---
title: "network"
author: "Miao YU"
date: '2018-10-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(WGCNA);
#Read in the female liver data set
femData = LiverFemale3600
dim(femData)
names(femData)

datExpr0 = as.data.frame(t(femData[, -c(1:8)]))
names(datExpr0) = femData$substanceBXH
rownames(datExpr0) = names(femData)[-c(1:8)]

gsg = goodSamplesGenes(datExpr0, verbose = 3);
gsg$allOK

if (!gsg$allOK)
{
  # Optionally, print the gene and sample names that were removed:
  if (sum(!gsg$goodGenes)>0) 
     printFlush(paste("Removing genes:", paste(names(datExpr0)[!gsg$goodGenes], collapse = ", ")));
  if (sum(!gsg$goodSamples)>0) 
     printFlush(paste("Removing samples:", paste(rownames(datExpr0)[!gsg$goodSamples], collapse = ", ")));
  # Remove the offending genes and samples from the data:
  datExpr0 = datExpr0[gsg$goodSamples, gsg$goodGenes]
}

sampleTree = hclust(dist(datExpr0), method = "average")

plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5, 
     cex.axis = 1.5, cex.main = 2)
clust = cutreeStatic(sampleTree, cutHeight = 15, minSize = 10)
keepSamples = (clust==1)
datExpr = datExpr0[keepSamples, ]
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)
```

```{r}
traitData = ClinicalTraits
dim(traitData)
names(traitData)

# remove columns that hold information we do not need.
allTraits = traitData[, -c(31, 16)];
allTraits = allTraits[, c(2, 11:36) ];
dim(allTraits)
names(allTraits)

# Form a data frame analogous to expression data that will hold the clinical traits.

femaleSamples = rownames(datExpr);
traitRows = match(femaleSamples, allTraits$Mice);
datTraits = allTraits[traitRows,]
tibble::column_to_rownames(datTraits, var = "Mice")
collectGarbage()

save(datExpr, datTraits, file = "FemaleLiver-01-dataInput.RData")
```

```{r}
enableWGCNAThreads()
lnames = load(file = "FemaleLiver-01-dataInput.RData");
#The variable lnames contains the names of loaded variables.
lnames

powers = c(c(1:10), seq(from = 12, to=20, by=2))
sft = pickSoftThreshold(datExpr, powerVector = powers, verbose = 5)

net = blockwiseModules(datExpr, power = 6,
TOMType = "unsigned", minModuleSize = 30,
reassignThreshold = 0, mergeCutHeight = 0.25,
numericLabels = TRUE, pamRespectsDendro = FALSE,
saveTOMs = TRUE,
saveTOMFileBase = "femaleMouseTOM",
verbose = 3)

moduleLabels = net$colors
moduleColors = labels2colors(net$colors)
MEs = net$MEs;
geneTree = net$dendrograms[[1]];

# Define numbers of genes and samples
nGenes = ncol(datExpr);
nSamples = nrow(datExpr);
# Recalculate MEs with color labels
MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes
MEs = orderMEs(MEs0)
moduleTraitCor = cor(MEs, datTraits, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);

sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
labeledHeatmap(Matrix = moduleTraitCor,
xLabels = names(datTraits),
yLabels = names(MEs),
ySymbols = names(MEs),
colorLabels = FALSE,
colors = greenWhiteRed(50),
textMatrix = textMatrix,
setStdMargins = FALSE,
cex.text = 0.5,
zlim = c(-1,1),
main = paste("Module-trait relationships"))
```

```{r}
no.obs=50
# now we specify the true measures of eigengene significance
# recall that ESturquoise=cor(y,MEturquoise)
ESturquoise=0; ESbrown= -.6;
ESgreen=.6;ESyellow=0
# Note that we dont specify the eigengene significance of the blue module
# since it is highly correlated with the turquoise module.
ESvector=c(ESturquoise,ESbrown,ESgreen,ESyellow)
# number of genes
nGenes1=3000
# proportion of genes in the turquoise, blue, brown, green, and yellow module #respectively.
simulateProportions1=c(0.2,0.15, 0.08, 0.06, 0.04)
# Note that the proportions dont add up to 1. The remaining genes will be colored grey,
# ie the grey genes are non-module genes.
# set the seed of the random number generator. As a homework exercise change this seed.
set.seed(1)
#Step 1: simulate a module eigengene network.
# Training Data Set I
MEgreen=rnorm(no.obs)
scaledy=MEgreen*ESgreen+sqrt(1-ESgreen^2)*rnorm(no.obs)
y=ifelse( scaledy>median(scaledy),2,1)
MEturquoise= ESturquoise*scaledy+sqrt(1-ESturquoise^2)*rnorm(no.obs)
# we simulate a strong dependence between MEblue and MEturquoise
MEblue= .6*MEturquoise+ sqrt(1-.6^2) *rnorm(no.obs)
MEbrown= ESbrown*scaledy+sqrt(1-ESbrown^2)*rnorm(no.obs)
MEyellow= ESyellow*scaledy+sqrt(1-ESyellow^2)*rnorm(no.obs)
ModuleEigengeneNetwork1=data.frame(y,MEturquoise,MEblue,MEbrown,MEgreen, MEyellow)
```

```{r}
dat1=simulateDatExpr5Modules(MEturquoise=ModuleEigengeneNetwork1$MEturquoise,
MEblue=ModuleEigengeneNetwork1$MEblue,
MEbrown=ModuleEigengeneNetwork1$MEbrown,
MEyellow=ModuleEigengeneNetwork1$MEyellow,
MEgreen=ModuleEigengeneNetwork1$MEgreen,
nGenes=nGenes1,
simulateProportions=simulateProportions1)

datExpr = dat1$datExpr;
truemodule = dat1$truemodule;
datME = dat1$datME;
attach(ModuleEigengeneNetwork1)

datExpr=data.frame(datExpr)
ArrayName=paste("Sample",1:dim(datExpr)[[1]], sep="" )
# The following code is useful for outputting the simulated data
GeneName=paste("Gene",1:dim(datExpr)[[2]], sep="" )
dimnames(datExpr)[[1]]=ArrayName
dimnames(datExpr)[[2]]=GeneName
```

```{r}
blockwiseModules(datExpr = (data_m), 
            checkMissingData = FALSE, blocks = mycl_metabs, 
            maxBlockSize = 5000, blockSizePenaltyPower = 100, 
            randomSeed = 12345, loadTOM = FALSE, corType = "pearson", 
            maxPOutliers = 1, quickCor = 0, pearsonFallback = "individual", 
            cosineCorrelation = FALSE, power = power_val, 
            networkType = "unsigned", TOMType = "signed", 
            TOMDenom = "min", getTOMs = NULL, saveTOMs = FALSE, 
            saveTOMFileBase = "blockwiseTOM", deepSplit = deepsplit, 
            detectCutHeight = NULL, minModuleSize = minclustsize, 
            maxCoreScatter = NULL, minGap = NULL, maxAbsCoreScatter = NULL, 
            minAbsGap = NULL, minSplitHeight = NULL, minAbsSplitHeight = NULL, 
            useBranchEigennodeDissim = FALSE, minBranchEigennodeDissim = mergeCutHeight, 
            stabilityLabels = NULL, minStabilityDissim = NULL, 
            pamStage = TRUE, pamRespectsDendro = FALSE, reassignThreshold = 1e-06, 
            minCoreKME = 0.5, minCoreKMESize = minclustsize/3, 
            minKMEtoStay = 0.3, mergeCutHeight = cutheight, 
            impute = TRUE, trapErrors = FALSE, numericLabels = FALSE, 
            nThreads = num_nodes, verbose = 0, indent = 0)
```

```{r}
```{r eval = F}
library(pmd)
data("spmeinvivo")
li <- globalstd(spmeinvivo)
data <- li$data[li$stdmassindex,]
library(qgraph)
cormat <- cor_auto(t(data))
Graph_pcor <- qgraph(cormat, graph = "pcor", layout = "spring")
Graph_pcor <- qgraph(cormat, graph = "pcor", layout = "spring", threshold = "bonferroni",
                     sampleSize = nrow(data), alpha = 0.05)
Graph_lasso <- qgraph(cormat, graph = "glasso", layout = "spring", tuning = 0.25,
                      sampleSize = nrow(data))
```
```

